Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-07 paper-v1.tex
Update tech refs by @naszam

\begin{itemize}
\item reproducibility crisis (a fix)
\item openness of access and data 
\item 'blockchainefied science':  "a more flexible, grass-root and reputation-based governance of science."
\end{itemize}
reputation metrics -- "blockchain would make much larger parts of the research cycle open to scientific self-correction. This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’. Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation." https://docs.google.com/document/d/1Uhjb4K69l0bSx7UXYUStV_rjuPC7VGo0ERa-7xEsr58/edit#heading=h.z4w0uvttpvgt
Decentralized
Distributed 
Immutable (≈’append only database’)
Transparent (provable to the external world)
"One such system, the Ethereum blockchain, goes so far as to provide its own programming language to run distributed, unstoppable, and provable applications [27]. This includes smart contracts [28] which can be used to realize distributed, autonomous applications and organizations [29]." they propose permissioned public blockchain for science
"Figure 3: Large parts of the research cycle can make use of blockchain (yellow arch); only the experiment/initial data collection itself cannot. From data collection onwards, the rest of the research circle would then become immutable, comprehensible, and externally provable. This would make larger parts of the research cycle open to scientific self-correction and may make more research results reproducible, true, and useful."
\begin{itemize}
\item scientific ideas/data/lab notebooks via time-stamping and proof of existence - Blockchains provide a ‘notarization’ functionality.
\item pre-registration in open science, now managed by open platforms like OSF 
\item The recommendation to reduce waste in science which reads: ‘Public availability of raw data and complete scripts of statistical analysis could be required by journals and funding agencies sponsoring new research’ [5,49] could be realized through blockchain. 
to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
\item stress on scientific self-correction: from open data science to blockchain based science 
\end{itemize}
"Figure 5: In closed science, scientists just publish a description of their research data and results in their final publication (I). Currently, researchers can publish their research data in data repositories, but that leaves no trace of the data collection or handling process (II). Of course, the final repository could be a blockchain based, decentralized database (III). However, blockchain technology could take the whole process one step further: the whole data handling process could take place in a blockchain system and would therefore be provable and open to scientific self-correction (at will) (IV)." 
Blockchain systems make it possible to publish research anonymously [70] or with a second online identity - and yet one could still get money or other research impact appreciation for it [71,72]
Science reputation systems can be built using blockchain without a trusted third party. 
As such, a Decentralized Autonomous Academic Endorsement System has been proposed and interesting implementation ideas and next implementation steps have been disclosed [72].
Research funding: A DARO (distributed autonomous research organization) allocates and distributes research resources.
could also engage the public through a more transparent research process. 
token economy could be applied to scientific ideas and groundbreaking discoveries, we could incentivise scientist to spread ideas early and strongly. This stands in contrast to the current system, which incentivises scientists to remain inert until publication, patent application, etc. It has been claimed that this could also be a solution to the famous innovators dilemma [9
What should token for science/research projects represent? One thing would be ‘asset-backed’ tokens as described here [96] as a bet on the commercially usable part of the intellectual property. However, is that enough? Couldn't there be tokens that represent a purely scientific value of a research project? Researchers are used to immaterial rewards called “reputation”. For instance, I could place bets (as outlined below on relativity and will receive reputation tokens for properly predicting outcomes. I would also receive “reputation” if my own research results can be validated by “the crowd” or will be used by their future work, i.e. represent the equivalent of citations.)  
The blockchain revolution is a game changer and hence chances are that this can be used to break with inappropriate cultures. Indeed, blockchain technology could be used to ‘Increase value and reduce waste’ [5], by opening the research cycle to scientific self-control beyond the final publication and might therefore be a fix to the current reproducibility crisis in science.

@@

\newline The paper is structured as follows. Sections 2 presents research background and related works. Section 3 explains the proposed Ethereum-based protocol illustrating the system architecture and the current status of implementation. In Sect. 4 we discuss the implication of our work. Section 5 contains the conclusions. Appendixes present the smart contracts.

@@

\newline The AntsReview Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:

@@

AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library\cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
\newline In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document"\cite{TimeStamp-Haber}
\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin\cite{Bitcoin} as its first application.
\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).

\subsubsection{Tokenomics

AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline \textbf{Ant}, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
\newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \textbf{\emph{Ant}} ans symbol: \textbf{\emph{ANT}}.
\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai, Chai \cite{Chai}, ... with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR or Compound to cite a few.
\newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
\newline \textbf{Hive}. When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
\newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
\newline \textbf{zkAnt}, is an Ant token wrapped into AZTEC Protocol ZK-SNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
\newline zkAnt will be implemented via AZTEC 2.0 that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
\newline Finally, another concept under investigation is Quadratic Funding, used by Gitcoin to match donations for Grants. This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.

@@

\section{AntsReviewRoles.sol}
\label{appendix:a}

@@

\newpage
\section{AntsReview.sol}
\label{appendix:b}

>>>>

\begin{itemize}
\item reproducibility crisis (a fix)
\item openness of access and data 
\item 'blockchainefied science':  "a more flexible, grass-root and reputation-based governance of science."
\end{itemize}
reputation metrics -- "blockchain would make much larger parts of the research cycle open to scientific self-correction. This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’. Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation."
Decentralized
Distributed 
Immutable (’append only database’)
Transparent (provable to the external world)
"One such system, the Ethereum blockchain, goes so far as to provide its own programming language to run distributed, unstoppable, and provable applications [27]. This includes smart contracts [28] which can be used to realize distributed, autonomous applications and organizations [29]." they propose permissioned public blockchain for science
"Figure 3: Large parts of the research cycle can make use of blockchain (yellow arch); only the experiment/initial data collection itself cannot. From data collection onwards, the rest of the research circle would then become immutable, comprehensible, and externally provable. This would make larger parts of the research cycle open to scientific self-correction and may make more research results reproducible, true, and useful."

\begin{itemize} 
\item scientific ideas/data/lab notebooks via time-stamping and proof of existence - Blockchains provide a ‘notarization’ functionality.
\item pre-registration in open science, now managed by open platforms like OSF 
\item The recommendation to reduce waste in science which reads: ‘Public availability of raw data and complete scripts of statistical analysis could be required by journals and funding agencies sponsoring new research’ [5,49] could be realized through blockchain. 
to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)
\item stress on scientific self-correction: from open data science to blockchain based science 
\end{itemize}

"Figure 5: In closed science, scientists just publish a description of their research data and results in their final publication (I). Currently, researchers can publish their research data in data repositories, but that leaves no trace of the data collection or handling process (II). Of course, the final repository could be a blockchain based, decentralized database (III). However, blockchain technology could take the whole process one step further: the whole data handling process could take place in a blockchain system and would therefore be provable and open to scientific self-correction (at will) (IV)." 
Blockchain systems make it possible to publish research anonymously [70] or with a second online identity - and yet one could still get money or other research impact appreciation for it [71,72]
Science reputation systems can be built using blockchain without a trusted third party. 
As such, a Decentralized Autonomous Academic Endorsement System has been proposed and interesting implementation ideas and next implementation steps have been disclosed [72].
Research funding: A DARO (distributed autonomous research organization) allocates and distributes research resources.
could also engage the public through a more transparent research process. 
token economy could be applied to scientific ideas and groundbreaking discoveries, we could incentivise scientist to spread ideas early and strongly. This stands in contrast to the current system, which incentivises scientists to remain inert until publication, patent application, etc. It has been claimed that this could also be a solution to the famous innovators dilemma [9
What should token for science/research projects represent? One thing would be ‘asset-backed’ tokens as described here [96] as a bet on the commercially usable part of the intellectual property. However, is that enough? Couldn't there be tokens that represent a purely scientific value of a research project? Researchers are used to immaterial rewards called “reputation”. For instance, I could place bets (as outlined below on relativity and will receive reputation tokens for properly predicting outcomes. I would also receive “reputation” if my own research results can be validated by “the crowd” or will be used by their future work, i.e. represent the equivalent of citations.)  
The blockchain revolution is a game changer and hence chances are that this can be used to break with inappropriate cultures. Indeed, blockchain technology could be used to ‘Increase value and reduce waste’ [5], by opening the research cycle to scientific self-control beyond the final publication and might therefore be a fix to the current reproducibility crisis in science.

@@

 The paper is structured as follows. Sections 2 presents research background and related works. Section 3 explains the proposed Ethereum-based protocol illustrating the system architecture and the current status of implementation. In Sect. 4 we discuss the implication of our work. Section 5 contains the conclusions. Appendixes present the smart contracts.

@@

The AntsReview Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart [Fig. \ref{fig:contracts}]:

@@

AntsReviewRoles[\ref{appendix:a}], to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library \cite{OZ}, through the creation of the Roles Issuer and Peer-Reviewer.
\newline It also integrates a circuit breaker design pattern via Pausable.sol by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the Smart Contracts, to pause (or unpause) the functions in case of emergency.
\newline In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta with the paper "How to time-stamp a digital document"\cite{TimeStamp-Haber}
\newline As the pioneers of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin\cite{Bitcoin} as its first application.
\newline In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree containing representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash.
\newline In order to verify if a specific hash is included into a Merkle Tree, leveraging on MerkleProof.sol by OpenZeppelin Library, we need to provide a proof, generated from the leaf of interest, that represent the remification derived from the leaf, the root hash and finally the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity \cite{Solidity}, an object-oriented programming language for writing smart contracts that run on the Ethereum Virtual Machine (EVM).

\subsubsection{Tokenomics}

AntsReview has few tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline \textbf{Ant}, is the primary protocol token and can be staked into an AntReview if you wish to provide the protocol with an additional security promise.
\newline Ant [\ref{appendix:c}] is implemented by inheriting ERC20PresetMinterPauser.sol from OpenZeppelin Library with name: \textbf{\emph{Ant}} ans symbol: \textbf{\emph{ANT}}.
\newline An AntReview, issued by an author will be seen as a poll where Anters (members of the AntsReview Community) can stake ether or tokens from DeFi services including Dai \cite{Dai}, Chai \cite{Chai}, ... with the possibility to accrue interest for the duration of an AntReview (1 year on average), via MakerDAO DSR \cite{DSR} or Compound to cite a few.
\newline An \textbf{AntsReview DAO} will be formed in the future to allow Ant stakers the ability to participates in a Decentralized Autonomous Organization which will be used to govern important aspects of the decentralized protocol, from smart contracts upgrades to more minor changes in settings across the protocol.
\newline \textbf{Hive}. When an Anter deposits into an AntReview, they will instantly receive the Hive token which represents their deposit and the accrued interest it gains over time in the AntReview.
\newline This token doesn't need to be locked in the network and it can be traded, sold, or held as the Anter desires.
\newline Hive will be implemented using a similar approach to Ant and Chai, a token that accrues interest from MakerDAO's DSR (Dai Saving Rate), with name: \textbf{\emph{Hive}} and symbol: \textbf{\emph{HIVE}}
\newline Ideally, but is still under investigation, after the deadline of the AntReview is reached, the Hive token will be burned for Ant and wrapped into zkAnt to allow anonymity and send equally to the peer-reviewers that fulfilled the AntReview.
\newline \textbf{zkAnt}, is an Ant token wrapped into AZTEC Protocol ZK-SNARKs, that will be extended to PLONK Proof to collapse the gas costs of private transactions on mainnet.
\newline zkAnt will be implemented via AZTEC 2.0 that will allow to securely wrap the Ant Token into zkAnt, allowing private transactions on mainnet and preserving the anonymity of Peer Reviewers.
\newline Finally, another concept under investigation is Quadratic Funding, used by Gitcoin to match donations for Grants. This will allow to incentives prolific Peer-Reviewers and improve the stability of the system together with ideally a reward system to rank best Peer-Reviewers.

@@

\section{AntsReviewRoles.sol}

\label{appendix:a}

@@

\newpage
\section{AntsReview.sol}

\label{appendix:b}
